Project Notes

### 2020-04-03 notes/notes.tex
Notes: update 03/04/2020

@@

TODO

@@

@@

\subsection{Integration tests}
For a given protocol and specified role/target,
generate the TypeScript code, put into the
sandbox environment and run \texttt{npm test} 
(which is just a wrapper for 
\texttt{tsc --noEmit})
to expect success return code.

>>>>

\paragraph{04/04/2020 [tomorrow]}
\begin{itemize}
\item
Focus on getting React code generation to work -- 
TicTacToe example for the receive handlers weren't
generalised enough, go back to OneNote to sketch
the encoding before trying it in code.
\end{itemize}

@@

TODO - on OneNote

@@

TODO - on OneNote

@@

\subsection{Integration tests}
TODO -- integrate with external components, namely
scribble-java (which would be mocked in unit tests).

\subsection{Systems tests}
For a given protocol and specified role/target,
generate the TypeScript code, put into the
sandbox environment and run \texttt{npm test} 
(which is just a wrapper for 
\texttt{tsc --noEmit})
to expect success return code.
